An Open Platform for Managing Short Programming Exercises

### 2013-06-19 paper/paper.tex
acknowedge special projects grant
tweak placement of fig.1
added a couple discussion questions

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=5.5in]{images/screenshot4}
\caption{Screenshot of the main view in CloudCoder}
\label{screenshot}
\end{figure*}

@@

\section{Discussion}

We could use community input into the CloudCoder project.  Specifically:

\begin{itemize}
\item Who would be interested in adopting this system?  If you would
  consider trying out the system if we added a particular feature,
  what would that feature be?  We would like
  to expand our pilot group.
\item What studies could or should be done with this platform?  And
  would you like to be involved with these studies?
\item What studies can be done with the existing data we have
  collected?  We do not yet have well-developed tools for data
  analysis, but one data set has been anonymized and can be
  distributed to other researchers interested in our data.
\end{itemize}

@@

Anonymized.

>>>>

\begin{figure*}
\centering
\includegraphics[width=5.5in]{images/screenshot4}
\caption{Screenshot of the main view in CloudCoder}
\label{screenshot}
\end{figure*}

@@

@@

\section{Discussion Questions}

%We could use community input into the CloudCoder project.  Specifically:
%
%\begin{itemize}
%\item Who would be interested in adopting this system?  If you would
%  consider trying out the system if we added a particular feature,
%  what would that feature be?  We would like
%  to expand our pilot group.
%\item What studies could or should be done with this platform?  And
%  would you like to be involved with these studies?
%\item What studies can be done with the existing data we have
%  collected?  We do not yet have well-developed tools for data
%  analysis, but one data set has been anonymized and can be
%  distributed to other researchers interested in our data.
%\end{itemize}

There are a number of questions, both philosophical and research-oriented,
that we would like to address in the context of our future work with CloudCoder.

{\bf Can the adoption of programming exercises lead to improved outcomes
in introductory programming courses?}  This is the most obvious
question.  One scenario we are particularly interested in is whether
the use of programming exercises, when {\em added} to an existing course with
no other changes in pedagogy, lead to improved outcomes.  We feel
that this scenario is important because educators have limited time
and resources available to change the way their courses are taught.
If programming exercises are an easy change to implement, then
if adopted on a wide scale they could have a significant impact.

{\bf Can exercises be reused effectively outside of the course in which
they were originally created?}  When assigning a programming exercise to
students, the instructor can create one from scratch, or use a
previously-written exercise.  Since creating good exercises is labor-intensive,
being able to use a previously-written exercise represents a significant
time savings.  However, finding an existing exercise that is {\em appropriate}
is not necessarily a trivial task.  We are interested in finding
out whether exercises written in the context of one course can be reused
effectively in another.

@@

Our work has been supported by a SIGCSE Special Projects grant (May 2012).
